Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-21 article.tex
Remove mention of stoichiometry in Species

For the reaction networks, our focus is on first-order differential
equations that describe the rate of change of species. SimBio simplifies
the definition of these network models by introducing \texttt{Species},
which consists of a \texttt{poincare.Variable} and a stoichiometric
number, and \texttt{RateLaw}, a construct that converts reactants into
products taking into account the stoichiometry
(Figure~\ref{fig-simbio}). Additionally, SimBio features
\texttt{MassAction}, a subclass of \texttt{RateLaw}, that intuitively
incorporates reactants into the rate law (Figure~\ref{fig-simbio}).

>>>>

For the \acp{CRN},
our focus is on first-order differential equations that describe the rate of change of species.
SimBio simplifies the definition of these network models by introducing \texttt{Species},
and \texttt{RateLaw}, a construct that converts reactant species into product species taking into account the stoichiometry (Figure~\ref{fig-simbio}).
Additionally, SimBio features \texttt{MassAction},
a subclass of \texttt{RateLaw},
that intuitively incorporates reactants and their stoichiometry into the rate law (Figure~\ref{fig-simbio}).
